\chapter{Design}

\section{Game Concept}

The game is a recreation of the classic \textit{Flappy Bird} mobile game, featuring \textbf{AV Eder} as the playable bird character. The player controls Eder by tapping or clicking to make him flap and stay airborne, while navigating through gaps between pipes. The goal is to survive as long as possible and achieve the highest score.

\section{Art Style}

The visual design follows a pixel art aesthetic, staying true to the original Flappy Bird's retro charm while incorporating custom character designs.

\subsection{Design Tools}

All pixel art assets were created using \textbf{Aseprite}, a professional pixel art and animation tool. Aseprite was chosen for its:
\begin{itemize}
    \item Intuitive pixel-perfect drawing tools
    \item Layer management for complex sprites
    \item Animation timeline for sprite animations
    \item Export options optimized for game engines
\end{itemize}

\section{Character Design}

\subsection{AV Eder (The Bird)}

The main character, AV Eder, replaces the traditional Flappy Bird with a custom-designed pixel art representation. The character was designed to be:
\begin{itemize}
    \item Recognizable and charming
    \item Appropriately sized for gameplay visibility
    \item Animated with smooth flapping motion
\end{itemize}

\section{Environment Design}

\subsection{Pipes}

The iconic green pipes serve as the main obstacles. They were designed with:
\begin{itemize}
    \item Clear visual boundaries for fair collision detection
    \item Consistent sizing for predictable gameplay
    \item Classic styling with a modern pixel art touch
\end{itemize}

\subsection{Background}

The background features a sundown sky theme, creating a warm and inviting atmosphere for the game. The design includes gradient colors transitioning from warm oranges to cooler blues.

\subsection{Coins}

Collectible coins were added as bonus items throughout the game. They feature:
\begin{itemize}
    \item Bright, eye-catching design
    \item Subtle bounce animation for visual feedback
    \item Clear visibility against the background
\end{itemize}

\section{User Interface}

The UI design prioritizes clarity and simplicity:
\begin{itemize}
    \item \textbf{Start Menu:} Displays game title and player statistics
    \item \textbf{In-Game HUD:} Shows current score and coins collected
    \item \textbf{Game Over Screen:} Presents final score, high score, and restart option
\end{itemize}

All UI elements were designed with readable fonts and semi-transparent panels for better visibility against the game background.
